---
title: "Survey Results Task 3.3 Part C and D"
author: "Anja Rainer"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    keep_md: true
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, dpi = 300)

df <- tar_read(with_countries)

question_codes <- read_csv("data/processed/question_codes.csv")
```

# C1 Institution: OA policy

Does your institution have an open access policy? (Y/N/ I don’t know)

```{r c1, fig.width=6, fig.height=2}

answer_levels_5 <- c("I don't know", "No", "Yes")

c1_df <- df %>% 
  select("C1")

c1_df_rec <- c1_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_5))


c1_df_rec %>% 
  plot_bar(C1, title = "Institution: OA policy", reorder = TRUE, nudge_y = .08)

```

# C3 Institution: OS/OA practices recommandation

Does your institution recommend open science/ open access practices? (Y/N)

```{r c3, fig.width=6, fig.height=2}

answer_levels_6 <- c("No", "Yes")

c3_df <- df %>% 
  select("C3")

c3_df_rec <- c3_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_6))


c3_df_rec %>% 
  plot_bar(C3, title = "Institution: OS/OA practices recommandation", reorder = TRUE, nudge_y = .08)

```

# c5 Helpdesk/group to support any issues

Is there a dedicated helpdesk/ group to support any issues related to the open science / open access policy? (Y/N/ I don’t know)

```{r c5, fig.width=6, fig.height=2}
c5_df <- df %>% 
  select("C5")

c5_df_rec <- c5_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_5))


c5_df_rec %>% 
  plot_bar(C5, title = "Helpdesk/group to support any issues", reorder = FALSE, nudge_y = .06)

```


# C6 Guidance on how to comply with the policies by the financing entities that require OA to publications

Do you receive any guidance on how to comply with the policies issued by the financing entities that require open access to publications, such as the European Commission or the European Research Council? (Y/N/ I don’t know)

```{r c6, fig.width=6, fig.height=2}

c6_df <- df %>% 
  select("C6")

c6_df_rec <- c6_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_5))

c6_df %>% 
  summarise(across(.fns = ~sum(is.na(.x))))

c6_df_rec %>% 
  plot_bar(C6, title = "Guidance on how to comply with the policies by the financing entities that require OA to publications", reorder = FALSE, nudge_y = .06)

```

# C7 Financial support in paying article processing charges (APCs)

Does your institution support you financially in paying article processing charges (APCs)? (Y/N/ I don’t know))

```{r c7, fig.width=6, fig.height=2}

c7_df <- df %>% 
  select("C7")

c7_df_rec <- c7_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_5))

c7_df %>% 
  summarise(across(.fns = ~sum(is.na(.x))))

c7_df_rec %>% 
  plot_bar(C7, title = "Financial support in paying article processing charges (APCs)", reorder = FALSE, nudge_y = .07)


```


# C8 Degree of support in practicing OS at institution

To what degree are you supported in practicing Open Science at your institution?

```{r c8, fig.width=9, fig.height=6, results="asis"}

answer_levels_7 <- c("Don’t know/ Don’t have enough information", "I do not receive any support or incentives", "I do not receive any support or incentives but would like to", "I receive some support or incentives", 
"I receive sufficient support or incentives")

c8_df <- df %>% 
  select(starts_with("C8[")) 

c8_df_rec <- c8_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_7))


c8_df %>% 
  summarise(across(.fns = ~sum(is.na(.x))))


c8_df_rec %>% 
  plot_likert()



```


# C10: Other initiatives incentivising Open Science practices at institution

Are there other initiatives incentivising Open Science practices at your institution (eg. Open Science cafes, Data champions)? (Y/N)

```{r c10, fig.width=6, fig.height=2}

c10_df <- df %>% 
  select("C10")

c10_df_rec <- c10_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_6))

c10_df %>% 
  summarise(across(.fns = ~sum(is.na(.x))))

c10_df_rec %>% 
  plot_bar(C10, title = "Other initiatives incentivising Open Science practices at institution", reorder = FALSE, nudge_y = .08)


```

# Part D: Drivers and barriers to practicing Open Science

# D2 Summarised views: What would you say OS is?

Overall, if you had to summarise your views, what would you say Open Science is?

```{r d2, fig.width=8, fig.height=8, results="asis"}

d2_df <- df %>% 
  select("D2[SQ001]", "D2[SQ002]", "D2[SQ003]", "D2[SQ004]", "D2[SQ005]", "D2[SQ006]", "D2[SQ007]")

d2_df_rec <- d2_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_6))

d2_df %>% 
  summarise(across(.fns = ~sum(is.na(.x))))


d2_df_rec %>% 
  plot_likert(legend_rows = 1)

```

# D3  Most significant barriers facing while embracing an OS perspective

Which are the most significant barriers you will be facing while embracing an Open Science perspective?

```{r d3, fig.width=8, fig.height=6, results="asis"}

answer_levels_8 <- c("Don’t know/ Don’t have enough information", "No barrier", "Minor barrier",
                     "Significant barrier", "Very significant barrier")

d3_df <- df %>% 
  select("D3[SQ001]", "D3[SQ002]", "D3[SQ003]", "D3[SQ004]", "D3[SQ005]", "D3[SQ006]", "D3[SQ007]", "D3[SQ008]")

d3_df_rec <- d3_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_8))

d3_df_rec %>% 
  plot_likert(legend_rows = 1)

```

# D5 Main drivers to participate OS

What could be the main drivers for you to practice open science?

```{r d5, fig.width=8, fig.height=8, results="asis"}

answer_levels_9 <- c("Don’t know/ Don’t have enough information", "No driver", "Minor driver",
                     "Significant driver", "Very significant driver")

d5_df <- df %>% 
  select(starts_with("D5[")) 

d5_df_rec <- d5_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_9))


d5_df %>% 
  summarise(across(.fns = ~sum(is.na(.x))))

d5_df_rec %>% 
  plot_likert(legend_rows = 1)


```

# D7 Drivers or barriers to practice Open Science

Would you say the following factors are drivers or barriers for you to practice Open Science?

```{r d7, fig.width=8, fig.height=8, results="asis"}

answer_levels_9 <- c("Don’t know/ Don’t have enough information", "Barrier", "Neither barrier nor driver",
                     "Driver")

d7_df <- df %>% 
  select(starts_with("D7[")) 

d7_df_rec <- d7_df %>% 
  mutate(across(.fns = factor, levels = answer_levels_9))


d7_df %>% 
  summarise(across(.fns = ~sum(is.na(.x))))

d7_df_rec %>% 
  plot_likert()

```